---
title: "Subadult Age Estimation Report"
---

```{r setup, echo=FALSE, message=FALSE}
library(pander)
library(caret)
library(dplyr)
```

```{r echo=FALSE, message=FALSE}
r_fdl <- if (!is.na(input$fdl)) paste(input$fdl) else paste("")
r_fmsb <- if (!is.na(input$fmsb)) paste(input$fmsb) else paste("")
r_fdb <- if (!is.na(input$fdb)) paste(input$fdb) else paste("")
r_tdl <- if (!is.na(input$tdl)) paste(input$tdl) else paste("")
r_tpb <- if (!is.na(input$tpb)) paste(input$tpb) else paste("")
r_tmsb <- if (!is.na(input$tmsb)) paste(input$tmsb) else paste("")
r_tdb <- if (!is.na(input$tdb)) paste(input$tdb) else paste("")
r_hdl <- if (!is.na(input$hdl)) paste(input$hdl) else paste("")
r_hpb <- if (!is.na(input$hpb)) paste(input$hpb) else paste("")
r_hmsb <- if (!is.na(input$hmsb)) paste(input$hmsb) else paste("")
r_hdb <- if (!is.na(input$hdb)) paste(input$hdb) else paste("")
r_rdl <- if (!is.na(input$rdl)) paste(input$rdl) else paste("")
r_rpb <- if (!is.na(input$rpb)) paste(input$rpb) else paste("")
r_rmsb <- if (!is.na(input$rmsb)) paste(input$rmsb) else paste("")
r_rdb <- if (!is.na(input$rdb)) paste(input$rdb) else paste("")
r_udl <- if (!is.na(input$udl)) paste(input$udl) else paste("")
r_umsb <- if (!is.na(input$umsb)) paste(input$umsb) else paste("")
```

Generated by KidStats on `r Sys.Date()`

Kyra Stull (2015). kidstats: Subadult age and sex estimations based on long bone measurements. R package version 0.0.1.9003. https://github.com/geanes/kidstats
  
----

## Input

- Reference sample: **`r switch(input$refsamp, 'za' = 'South Africa')`**
- Transformation on Age: **`r switch(input$transform, 'none' = 'None', 'sqrt' = 'Square root', 'cbrt' = 'Cube root')`**

<br>

#### Input measurements

|           | Diaphyseal Length | Proximal Breadth | Midshaft Breadth | Distal Breadth |
| :-------- | :---------------: | :--------------: | :--------------: | :------------: |
|   Femur   |     `r r_fdl`     |                  |    `r r_fmsb`    |    `r r_fdb`   |
|   Tibia   |     `r r_tdl`     |    `r r_tpb`     |    `r r_tmsb`    |    `r r_tdb`   |
|   Humerus |     `r r_hdl`     |    `r r_hpb`     |    `r r_hmsb`    |    `r r_hdb`   |
|   Radius  |     `r r_rdl`     |    `r r_rpb`     |    `r r_rmsb`    |    `r r_rdb`   |
|   Ulna    |     `r r_udl`     |                  |    `r r_umsb`    |                |

<br>

----

## Age Estimation

| Lower Prediction Interval |         Estimated Age        |  Upper Prediction Interval |
| :-----------------------: | :--------------------------: | :------------------------: |
|  `r earth_mod()[[2]][2]`  | **`r earth_mod()[[2]][1]`**  |   `r earth_mod()[[2]][3]`  |

<br>

### Model

- Sample size used to model: **`r nrow(age_samp())`**
- Age model Generalized R^2^: **`r round(earth_mod()[[1]]$grsq, digits = 4)`**
- Excluded measurements: `r if (length(input$ex_age) == 0) pander("none") else pander(input$ex_age)`

<br>

#### Coefficents and Hinge Points

```{r echo=FALSE, message=FALSE}
hinges <- add_rownames(data.frame(earth_mod()[[1]]$cuts), "Coefficients")
hinges <- hinges[earth_mod()[[1]]$selected.terms,]
pander(hinges)
```
